\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
{his/her -> her}

\emph{Spatial} perspective taking refers to the qualitative spatial location of
objects (or agents) with respect to a frame (\eg \emph{the keys on my left}).
Based on this frame of reference, the description of an object
varies~\cite{Marin2008}. Humans mix perspectives frequently during interaction.
This is more effective than maintaining a consistent one, either because the
(cognitive) cost of switching is lower than remaining with the same
perspective, or if the cost is about the same, because the spatial situation
may be more easily described from one perspective rather than
another~\cite{Tversky1999}. Ambiguities arise when one speaker refers to an
object within a reference system (or changes the reference system, \ie switches
perspective) without informing his/her partner about it~\cite{Breazeal2006,
Ros2010}. For example, the speaker could ask for the ``keys on the left''.
Since no reference system has been given, the listener would not know where
exactly to look.  However, asking for ``the keys on your left'' gives enough
information to the listener to understand where the speaker is referring to. On
the contrary, when using an exact, unambiguous term of reference to describe a
location (\eg. ``go north'') no ambiguity arises.
In {\sc Spark}, agent-dependent spatial relations are computed from the frame of
reference of each agent.

@@

\begin{itemize}
\item \emph{Reachable} enables the robot to estimate the agent's ability to
    reach for an object, which is instrumental for effective social task
    planning. For example, if the human asks the robot to give her an object,
    the robot must compute a transfer point where she is able to get the
    object afterwards.  Reachability is computed for each agent (human or robot) based on
    Generalised Inverse Kinematics and collision detection. More than that, our robot is able 
    to compute an estimate of the effort needed by an agent to reach an object\cite{pandey2013affordance}.

@@

Monitoring human activity is needed by the execution controllers to track the
engagement of the human and the progress of his/her actions and also to synchtronize seamlessly
its own actions with the human actions. Full human action
and activity recognition is a task that requires knowledge and reasoning both on
high-level facts like goals, intentions and plans, as well as bottom-up data
from human and object motions. {\sc Spark} implements a set of simple temporal and
geometric heuristics on human hand trajectories and possible objects placements
to recognize simple atomic actions. Those primitive actions are assessed through
monitoring situations like ``an empty hand is close to an object on a table''
(precursor for a \emph{pick}), or ``a hand holding an object is over a
container'' (precursor for a \emph{throw}).  {\sc Spark} recognises a set of
such primitives. When combined with the other geometric computations and a predictive
plan of the human actions (see Section~\ref{hatp}), the execution controller can
track the fulfilment of the pre- and post-conditions of the predicted human
actions. As a result, the robot can monitor the engagement of the human and the
overall progress of the human-robot shared plan.

@@

Additionally, temporal reasoning (essential for accurate action recognition for
instance) is not properly addressed in our architecture. Temporal reasoning is used
only locally, and does not allow for tracking of long sequences or global events.

@@

\emph{When to perform a given action} is enriched here by the human context
since it has to take into account the human, his/her needs, his/her rhythms and
pace, and his/her mental state. While performing its share of the task, the
robot has to produce signals directed towards the human and to respond to
signals produced back at the proper pace.

>>>>

\emph{Spatial} perspective taking refers to the qualitative spatial location of
objects (or agents) with respect to a frame (\eg \emph{the keys on my left}).
Based on this frame of reference, the description of an object
varies~\cite{Marin2008}. Humans mix perspectives frequently during interaction.
This is more effective than maintaining a consistent one, either because the
(cognitive) cost of switching is lower than remaining with the same
perspective, or if the cost is about the same, because the spatial situation
may be more easily described from one perspective rather than
another~\cite{Tversky1999}. Ambiguities arise when one speaker refers to an
object within a reference system (or changes the reference system, \ie switches
perspective) without informing her partner about it~\cite{Breazeal2006,
Ros2010}. For example, the speaker could ask for the ``keys on the left''.
Since no reference system has been given, the listener would not know where
exactly to look.  However, asking for ``the keys on your left'' gives enough
information to the listener to understand where the speaker is referring to. On
the contrary, when using an exact, unambiguous term of reference to describe a
location (\eg. ``go north'') no ambiguity arises.
In {\sc Spark}, agent-dependent spatial relations are computed from the frame of
reference of each agent.

@@

\begin{itemize}
\item \emph{Reachable} enables the robot to estimate the agent's ability to
    reach for an object, which is instrumental for effective social task
    planning. For example, if the human asks the robot to give her an object,
    the robot must compute a transfer point where she is able to get the
    object afterwards.  Reachability is computed for each agent (human or robot) based on
    Generalised Inverse Kinematics and collision detection. More than that, our robot is able 
    to compute an estimate of the effort needed by an agent to reach an object~\cite{pandey2013affordance}.

@@

Monitoring human activity is needed by the execution controllers to track the
engagement of the human and the progress of her actions and also to synchtronize seamlessly
its own actions with the human actions. Full human action
and activity recognition is a task that requires knowledge and reasoning both on
high-level facts like goals, intentions and plans, as well as bottom-up data
from human and object motions. {\sc Spark} implements a set of simple temporal and
geometric heuristics on human hand trajectories and possible objects placements
to recognize simple atomic actions. Those primitive actions are assessed through
monitoring situations like ``an empty hand is close to an object on a table''
(precursor for a \emph{pick}), or ``a hand holding an object is over a
container'' (precursor for a \emph{throw}).  {\sc Spark} recognises a set of
such primitives. When combined with the other geometric computations and a predictive
plan of the human actions (see Section~\ref{hatp}), the execution controller can
track the fulfilment of the pre- and post-conditions of the predicted human
actions. As a result, the robot can monitor the engagement of the human and the
overall progress of the human-robot shared plan.

@@

Additionally, temporal reasoning (essential for accurate action recognition for
instance) is not properly addressed in the current version of our system. Temporal reasoning is used
only locally, and does not allow for tracking of long sequences or global events.

@@

\emph{When to perform a given action} is enriched here by the human context
since it has to take into account the human, her needs, her rhythms and
pace, and her mental state. While performing its share of the task, the
robot has to produce signals directed towards the human and to respond to
signals produced back at the proper pace.
